Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-11 popl24/automation.tex
checkpoint

To obtain $\runs(\prog)$, we can perform a left folding of $\solve$
across $\prog$ and each view definition, inductively extending
memories with valid view assignments in the order of their definition.
We denote this computation as $\cruns(\prog)$.
\begin{lemma}
  \label{lemma-cruns}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define:
  \begin{eqnarray*}
    {tt}\ \ \stores\ (\eassign{\view{\cid}{w}}{\be}) &\defeq& \begin{array}{l}
      \mathrm{let}\ \stores' = \solve{\stores}{\be} \ \mathrm{in}\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{1} \mid \store \in \stores' \}\ \cup\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{0} \mid \store \in \stores - \stores' \}\end{array}\\[2mm]
    \cruns(\prog) &\defeq& \mathit{foldl}\ {tt}\ \mems(S \cup F)\ \prog
  \end{eqnarray*}
  Then $\cruns(\prog) = \runs(\prog)$.
\end{lemma}
\begin{proof}
  By Lemma \ref{lemma-solves} and induction on the length of $\prog$. 
\end{proof}
The above yields an algorithm for computing basic distributions and
thus program distributions. 
\begin{lemma}
  \label{lemma-cprogtt}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define
  $\cprogtt(\prog)$ as the distribution $\pmf$
  where for all $\store \in \mems(S\cup F \cup V)$:
  $$
  \pmf(\store) = 1 / 2^{|S\cup F|} \ \text{if}\ \store \in \cruns(\prog), \text{otherwise}\ 0
  %\begin{cases}1/2^{|S \cup F|} & \text{if\ } \store \in
  %  \cruns(\prog) \\ 0 & \text{otherwise} \end{cases} 
  $$
  Then $\cprogtt(\prog) = \progtt(\prog)$ and $\margd{\cprogtt(\prog)}{S\cup V} = \progd(\prog)$.
\end{lemma}
\begin{proof}
  Immediately by Lemma \ref{lemma-cruns} and Definition \ref{def-progd}.
\end{proof}
A full implementation of these methods is available in our online
repository \cite{jpdf-github}. To
avoid notational confusion we will continue to refer to $\progtt$ and
$\cruns$ in our subsequent discussion of automated verification but
with the understanding that both can be computed using the above
algorithms.

>>>>

To obtain $\runs(\prog)$, we can perform a standard left folding of $\solve{\!}{\!}$
across $\prog$ as a list of view definitions, inductively extending
memories with valid view assignments in the order of their definition.
We denote this computation as $\cruns(\prog)$.
\begin{lemma}
  \label{lemma-cruns}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define:
  \begin{eqnarray*}
    {tt}\ \ \stores\ (\eassign{\view{\cid}{w}}{\be}) &\defeq& \begin{array}{l}
      \mathrm{let}\ \stores' = \solve{\stores}{\be} \ \mathrm{in}\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{1} \mid \store \in \stores' \}\ \cup\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{0} \mid \store \in \stores - \stores' \}\end{array}\\[2mm]
    \cruns(\prog) &\defeq& \mathit{foldl}\ {tt}\ \mems(S \cup F)\ \prog
  \end{eqnarray*}
  Then $\cruns(\prog) = \runs(\prog)$.
\end{lemma}
\begin{proof}
  By Lemma \ref{lemma-solves} and induction on the length of $\prog$. 
\end{proof}
The above yields an algorithm for computing basic distributions and
thus program distributions. 
\begin{lemma}
  \label{lemma-cprogtt}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define
  $\cprogtt(\prog)$ as the distribution $\pmf$
  where for all $\store \in \mems(S\cup F \cup V)$:
  $$
  \pmf(\store) = 1 / 2^{|S\cup F|} \ \text{if}\ \store \in \cruns(\prog), \text{otherwise}\ 0
  %\begin{cases}1/2^{|S \cup F|} & \text{if\ } \store \in
  %  \cruns(\prog) \\ 0 & \text{otherwise} \end{cases} 
  $$
  Then $\cprogtt(\prog) = \progtt(\prog)$ and $\margd{\cprogtt(\prog)}{S\cup V} = \progd(\prog)$.
\end{lemma}
\begin{proof}
  Immediately by Lemma \ref{lemma-cruns} and Definition \ref{def-progd}.
\end{proof}
A full implementation of these methods is available in our online
repository \cite{jpdf-github}. To
avoid notational confusion we will continue to refer to $\progtt$ and
$\cruns$ in our subsequent discussion of automated verification but
with the understanding that both can be computed using the above
algorithms.

### 2023-07-11 popl24/composition.tex
checkpoint

\subsection{GMW Component Certification}

@@

\subsection{GMW Gate Invariants and Circuit Security}

@@

Our certification techniques are defined generally wrt implementations
of input encoding, decoding, and internal gates. In the following we
will refer to arbitrary decode, encode, and gate functions with the
restriction that any function in each of these categories has the same
valid type signature as $\ttt{decode}$, $\ttt{encode}$, and
$\ttt{andgg}$ respectively.

It is necessary to define notions of correlation with wire

@@

positive of negative correlation with them.

@@

  We write $\gc{\prog}{\{ \ttt{k = }\be_{k}; \ttt{p = }\be_{p} \}}{g}$ iff one of the

@@

  \item $\vc{\progtt(\prog,\be_k)}{\itv}{\ttt{flip[2,gate:}g\ttt{.k]}}\quad \text{and} \quad
    \vc{\progtt(\prog,\be_p)}{\itv}{\ttt{flip[2,gate:}g\ttt{.p]}}$
  \item $\vc{\progtt(\prog,\enot\ \be_k)}{\itv}{\ttt{flip[2,gate:}g\ttt{.k]}}\quad \text{and}\quad
    \vc{\progtt(\prog,\enot\ \be_p)}{\itv}{\ttt{flip[2,gate:}g\ttt{.p]}}$

@@

@@

    \item $\mathit{gate}\ttt{(c,a,b,owl(a),owl(b));}$
    \item $\mathit{gate}\ttt{(c,a,b,owl(a),invert(owl(b)));}$
    \item $\mathit{gate}\ttt{(c,a,b,invert(owl(a)),owl(b));}$
    \item $\mathit{gate}\ttt{(c,a,b,invert(owl(a)),invert(owl(b)))}$

@@

  $${\small X \defeq \ttt{\{ flip[2,gate:a.k], flip[2,gate:a.p], flip[2,gate:b.k], flip[2,gate:b.p] \}}}$$

@@

  \item For all $1 \le i \le 4$, $\gc{\prog}{v_i}{\ttt{c}}$

@@

  \config{\varnothing}{\ttt{encode(s1,s2)}} \redxs

@@

  \item $\gc{\prog}{v_1}{\ttt{s1}} \quad \text{and} \quad \gc{\prog}{v_2}{\ttt{s2}}$

@@

  \item All $x \in \vars(\prog)$ are distinguished by $\ttt{in1}$ or $\ttt{in2}$. 

@@

  \config{\varnothing}{\mathit{decode}(\ttt{c}, \ttt{owl(c)})}

@@

  \sep{\progtt(\prog)}{\ttt{\{flip[2,gate:c.k],flip[2,gate:c.p]\}}}{\vdefs(\prog)}

@@

\subsection{YGC Gate Invariants and Circuit Security}
\label{section-composition-metatheory}

To demonstrate correctness of certification, we need to show that
isolated component certificates preserve relevant properties
when integrated into larger programs. 
%First, we show that if a flip $f$ is independent from the views
%in a protocol (as is the case with input labels used to
%encode a garbled table), then separation from views that
%use $f$ (e.g., in an output label) is preserved. 
%\begin{lemma}[Wire Framing]
%  \label{lemma-wire-framing}
%  If $\sep{\progtt(\prog)}{\{f\}}{\vdefs(\prog)}$ for flip $f$ and
%  $\vars(\prog) \cap \vars(\prog') = \{ f \}$ then
%  $\sep{\progtt(\prog';\prog)}{\vdefs(\prog')}{\vdefs(\prog)}$.
%\end{lemma}
%Next,

Now we can show how to splice gates into arbitrary circuits in an
invariant-preserving manner, assuming that outputs are not wired to
multiple inputs \cite{tate2003garbled,nieminen2023breaking}.
\begin{restatable}[YGC Gate Invariant]{lemma}{ygcgate}
  \label{lemma-ygc-preservation}
Given well-typed $\prog_1;E[\mathit{gate}(g,g_1,g_2,v_1,v_2)]$ and certified $\mathit{gate}$ where:
$$
\config{\prog_1}{E[\mathit{gate}(g,g_1,g_2,v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
$$
If the following preconditions hold where $\iov(\prog_1) = S \cup V$:
\begin{enumerate}
\item $\{ g_1 \} \cap \{ g_2 \} \cap \wired(\prog_1) = \varnothing$ and $g \not\in \prog_1$
\item $\gc{\prog_1}{v_1}{g_1}$ and $\gc{\prog_1}{v_2}{g_2}$
\item $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$
\item $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$
\end{enumerate}
then we have as postconditions where $\iov(\prog_1) = S \cup V'$:
\begin{enumerate}
\item $\gc{\prog_1;\prog_2}{v}{g_2}$
\item $\sep{\progd(\prog_1,\prog_2)}{S_{\{1\}}}{V'_{\{2\}}}$
\item $\sep{\progd(\prog_1,\prog_2)}{S_{\{2\}}}{V'_{\{1\}}}$
\end{enumerate}
\end{restatable}

@@

Given the above, we can now establish that any circuit built with
certified components is passive secure.  Note that we assume a normal
form of programs where the last instruction is a decoding and public
reveal of the output, and we require that no gate is wired more than once.
\cnote{There is another subtlety here, that gates are wired correctly
  in the sense that if the garbler generates a table with input wire label
  $g_1$ then only $g_1$ is wired to that input. }
\begin{restatable}{theorem}{ygcnimo}
  \label{theorem-ygc-NIMO}
  If $\eassign{\outv}{\ttt{decode}(g,e)}$ is a well-typed YGC circuit
  definition using certified components where no gate output is wired
  more than once, and
  $\config{\varnothing}{\eassign{\outv}{\ttt{decode}(g,e)}} \redxs
  \config{\prog}{\varnothing}$, then $\NIMO(\prog)$.
\end{restatable}

>>>>

\subsection{GMW Component Certification}
\label{section-gmw-certification}

@@

\subsection{GMW Gate Invariants and Circuit Security}
\label{section-gmw-composition}

@@

In the case of YGC, wires are defined via wire labels as opposed
to shares as in GMW. It is necessary to define notions of correlation with wire

@@

positive of negative correlation with them, and this correlation is
integral to both pre-~and post-conditions of certification. We
write $\gc{\prog}{v}{g}$ to denote this, where $g$
is the gate with which $v$ has \emph{\bf g}arbled \emph{\bf o}utput
\emph{\bf c}orrelation.

@@

  We write $\gc{\prog}{\{ \ttt{k = }\be_{k}; \ttt{p = }\be_{p} \}}{\ttt{"g"}}$ iff one of the

@@

  \begin{enumerate}[\hspace{2mm}i.]
  \item $\vc{\progtt(\prog,\be_k)}{\itv}{\ttt{"flip[2,gate:g.k]"}}\ \, \text{and} \ \,
    \vc{\progtt(\prog,\be_p)}{\itv}{\ttt{"flip[2,gate:g.p]"}}$
  \item $\vc{\progtt(\prog,\enot\ \be_k)}{\itv}{\ttt{"flip[2,gate:g.k]"}}\ \, \text{and} \ \,
    \vc{\progtt(\prog,\enot\ \be_p)}{\itv}{\ttt{"flip[2,gate:g.p]"}}$

@@

Recall from Figure \ref{fig-ygc-lib} that $\ttt{owl("g")}$ returns
the output wire label of gate $\ttt{g}$ in a positive valence.

@@

    \item $\mathit{gate}\ttt{("c","a","b",owl("a"),owl("b"));}$
    \item $\mathit{gate}\ttt{("c","a","b",owl("a"),invert(owl("b")));}$
    \item $\mathit{gate}\ttt{("c","a","b",invert(owl("a")),owl("b"));}$
    \item $\mathit{gate}\ttt{("c","a","b",invert(owl("a")),invert(owl("b")))}$

@@

  $${\small X \defeq \ttt{\{ flip[2,"gate:a.k"], flip[2,"gate:a.p"], flip[2,"gate:b.k"], flip[2,"gate:b.p"] \}}}$$

@@

  \item For all $1 \le i \le 4$, $\gc{\prog}{v_i}{\ttt{"c"}}$

@@

  \config{\varnothing}{\mathit{encode}\ttt{("s1","s2")}} \redxs

@@

  \item $\gc{\prog}{v_1}{\ttt{"s1"}} \quad \text{and} \quad \gc{\prog}{v_2}{\ttt{"s2"}}$

@@

  \item All $x \in \vars(\prog)$ are distinguished by $\ttt{"s1"}$ or $\ttt{"s2"}$. 

@@

  \config{\varnothing}{\mathit{decode}(\ttt{"c"}, \ttt{owl("c")})}

@@

  \sep{\progtt(\prog)}{\ttt{\{flip[2,"gate:c.k"],flip[2,"gate:c.p"]\}}}{\vdefs(\prog)}

@@

\subsection{YGC Gate Invariants and Circuit Security}
\label{section-ygc-composition}

Now we demonstrate that certified gates preserve the desired invariant
during execution in arbitrary circuit contexts, assuming that outputs are not wired to
multiple inputs \cite{tate2003garbled,nieminen2023breaking}. That is, where
$\iov(\prog) = S \cup V$, we show that
$\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
$\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$ are preserved prior to
decoding.  We formulate this in terms of pre-~and post-conditions of
gate evaluation. Proofs omitted here are provided in Appendix
\ref{section-proofs}.

\begin{restatable}[YGC Gate Invariant]{lemma}{ygcgate}
\label{lemma-ygc-preservation}
Given well-typed $\prog_1;E[\mathit{gate}(g,g_1,g_2,v_1,v_2)]$ and certified $\mathit{gate}$ where:
$$
\config{\prog_1}{E[\mathit{gate}(g,g_1,g_2,v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
$$
If the following preconditions hold where $\iov(\prog_1) = S \cup V$:
\begin{enumerate}
\item $\{ g_1 \} \cap \{ g_2 \} \cap \wired(\prog_1) = \varnothing$ and $g \not\in \prog_1$
\item $\gc{\prog_1}{v_1}{g_1}$ and $\gc{\prog_1}{v_2}{g_2}$
\item $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$
\item $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$
\end{enumerate}
then we have as postconditions where $\iov(\prog_1) = S \cup V'$:
\begin{enumerate}
\item $\gc{\prog_1;\prog_2}{v}{g_2}$
\item $\sep{\progd(\prog_1,\prog_2)}{S_{\{1\}}}{V'_{\{2\}}}$
\item $\sep{\progd(\prog_1,\prog_2)}{S_{\{2\}}}{V'_{\{1\}}}$
\end{enumerate}
\end{restatable}

@@

Given the above, we can now establish that any circuit built with
certified components is passive secure.  Note that we assume a normal
form of programs where the last instruction is a decoding and public
reveal of the output, and we require that no gate is wired more than once.
\begin{restatable}{theorem}{ygcnimo}
  \label{theorem-ygc-NIMO}
  If $\eassign{\outv}{\ttt{decode}(g,e)}$ is a well-typed YGC circuit
  definition using certified components where no gate output is wired
  more than once, and
  $\config{\varnothing}{\eassign{\outv}{\ttt{decode}(g,e)}} \redxs
  \config{\prog}{\varnothing}$, then $\NIMO(\prog)$.
\end{restatable}
